Ricci

### 2014-10-30 prep_figures/distribution/ggvis.Rmd
Also looking via ggplot.

d <- read.table("../../results/ricci7.mat", stringsAsFactors=FALSE)
colnames(d) <- c("t1_idx", "t2_idx", "t1_nwk", "t2_nwk", "mult", "dist", "kappa_str")
d <- subset(d, kappa_str != "-")
d <- sample(d)  # Shuffle rows of d.
d$kappa <- sapply(d$kappa_str, function(s) eval(parse(text=s)))
d$info= paste(d$t1_nwk, d$t2_nwk, paste("kappa:", d$kappa_str), sep="<br />")
d$dist_jitter = d$dist + runif(nrow(d), min = -0.35, max = 0.35)

>>>>

source("process.R")

d <- get_results("../../results/ricci7.mat")
